Seismic parameter estimation and the Canadian crust

### 2013-07-06 static/draftBP.tex
working

  The preliminary interrogation of the data set yields the observation that the bulk Canadian Shield has lower Vp/Vs than anticipated. Previous experiments show crustal averages of 1.77 (Christensen and Mooney, 1995) and 1.78 (Zandt and Ammon, 1995). This compares to computed values of 1.73, 1.74, 1.795 for the Churchill, Superior and Grenville Provinces Vp/Vs ratios respectively.

(MIGHT NOT INCLUDE)  The data bares out earlier results showing Proterozoic crust to have a higher seismic velocity ratio than Archean crust. This follows previous studies on crustal formation that have noted this trend in other regions (Durrheim and Mooney, 1991) . The increased crustal thickness of Proterozoic crust is clearly seen in the active source data while it not visible in data from processed seismic stations.

  Further work on the Bostock-Kumar stacking approach is warranted from a look at the cleanest stations. Before it can be employed in large scale analysis additional denoising methods or alternative deconvolution techniques will need to be investigated to reduce the noise in the data.

>>>>

  - Comparison Discussion
    - Crustal Thickness
      - Very good correlation in thickness estimates with all three datasets.
    - Vp/Vs
      - Lower correlation with the Vp/Vs values.
        - Expect lower correlation with Vp/Vs since the travel time equations are
          less sensitive to seismic velocities than they are to crustal thickness.
          This means that there will be more uncertainty during the parameter
          search for Vp/Vs and hence higher degree of relative error.
        - ??? Utilizing different sources, applying different deconvolution and
          filtering techniques will therefore have a greater impact on the
          uncertainty of picking Vp/Vs than that of crustal thickness H. ???

   - Explanation of results
    - Canada H and Vp/Vs
      - Lith5.0 (Perry, 2002) estimates for Canadian crustal averages is 38 km. The Crust
        2.0 average is 38km as well, however this is expected since Crust2.0 data for
        Canada is based on the same data as that of Lith5.0
      - ??? Make some comparison to global average ???
